An Exegesis of Ontological Hermeneutics

### 2023-02-08 paper.tex
SNR and constellation wip

\newacronym{PL}{PL}{Path loss}
\newacronym{LOS}{LOS}{Line of sight}
\newacronym{NLOS}{NLOS}{Non-line of sight}

@@

\chapter{Multipath Channel Models}

\glsaddall
\printglossary[type=\acronymtype,title=Acronyms]

>>>>

\newacronym{PL}{PL}{Path loss}
\newacronym{LOS}{LOS}{Line of sight}
\newacronym{NLOS}{NLOS}{Non-line of sight}
\newacronym{BW}{BW}{Bandwidth}
\newacronym{iid}{i.i.d.}{independent and identically-distributed}
\newacronym{CLT}{CLT}{Central Limit Theorem}
\newacronym{GRV}{GRV}{Gaussian random variable}
\newacronym{SNR}{SNR}{signal-to-noise ratio}
\newacronym{PSD}{PSD}{power spectral density}
\glsaddall

@@

\chapter{Multipath Channel Models}
\label{multipath_ch_model}
A transmitted signal $s(t)$ propagates through an environment in multiple paths.
Neglecting noise, the received signal is simply a sum of attenuated, delayed,
and phase shifted versions of the original transmitted signal. The different
paths a signal takes to get to a receiver results in a sum with patterns of high
or low destructive interference, an effect called multipath fading.
\section{Multipath Model}
We model the channel $c(\tau,t)$ as a time-varying ($t$) impulse response function evaluated at $t - \tau$. As with any system, the received signal is modeled as a convolution of $c(\tau,t)$ with the transmitted signal $s(t)$.

A way to interpret the parameters is as follows:
\begin{itemize}
  \item $t$ is the time an impulse response is observed
  \item $\tau$ is the offset from the observation time in which the impulse was transmitted
\end{itemize}

The traditional impulse response of a time-invariant system can be expressed as
thinking of the channel's impulse response as periodic $c(\tau,t + T)$ where $T
  = -t$ such that  $c(\tau,0) = c(\tau)$, which is the impulse response at time
$0$.

Whether \gls{NLOS} received signals are received in a large spread of time
compared to the \gls{LOS} component or not, depends on the inverse of the
transmitted signal's \gls{BW}. This spread is called the delay spread $T_m$.
Depending on whether it is large or small changes the model significantly, so it
is explored as Narrowband and Wideband fading.

\section{Narrowband Fading Model}
Under this regime, the delay spread $T_m$ is significantly smaller than the inverse of the baseband \gls{BW} of the signal $B_{bb}$, $T_m << B^{-1}_{bb}$. Essentially, this model assumes that all paths have no delay as mentioned in Section \ref{multipath_ch_model}, but still have random phases. For a received signal $r(t)$, the following model is assumed,

\begin{align}
  r(t) = \operatorname{Re} \Biggl\{ s(t) e^{j2\pi f_c t} \left(\sum_i \alpha_i(t) e^{-j \phi_i(t)}\right) \Biggr\}
\end{align}
where $f_c$ is the carrier frequency, $\alpha_i$ are the attenuation on each path $i$ with their respective phase offset $\phi_i$.

For large $N(t)$ (time dependent number of multipath components) if $\alpha_i$ and $\phi_i$ are \gls{iid}, then by the \gls{CLT}, the real and imaginary components of the baseband equivalent received signal are approximately joint \glspl{GRV}. If some path is larger in amplitude, like the \gls{LOS} path, then the paths are no longer \gls{iid} so the \gls{CLT} no longer holds and the baseband components are not joint \gls{GRV}.

TODO Autocorrelation
\chapter{Channel Reliability}

\section{Signal Modulation}

TODO

\begin{figure*}[t]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/constellations.pdf}
  \caption{Constellation schemes where Quadrature and In-Phase possible discrete options are displayed in terms of their energy.}
  \label{fig:constellations}
\end{figure*}

\begin{table}[htbp]
  \centering
  \caption{}
  \begin{tabular}{lcccc}                                                                                                                   \\
    \cmidrule(r){1-5}  & MPAM                           & MPSK                       & MQAM                         & FSK     \\
    \midrule $E_s$     & $\frac{d_{min}^2}{12}(M^2-1)$  & $d^2$                      & $\frac{d_{min}^2}{6}(M^2-1)$ & $d^2/2$ \\
    \midrule $d_{min}$ & $\sqrt{\frac{12E_s}{M^2 - 1}}$
                       & $\sqrt{E_s}$                   & $\sqrt{\frac{6}{M^2 - 1}}$ & $\sqrt{2 E_s}$                         \\

    \bottomrule
  \end{tabular}
  \label{tab:win-space-results}
\end{table}

\section{Signal-to-noise ratio}

If the complex noise $n(t) \sim \mathcal{C}\mathcal{N}(0,2\sigma^2)$, meaning
each of the two channels is distributed as a zero-mean \gls{GRV} with variance
$\sigma$, this relates to the noise \gls{PSD} $N_0$ (in watts per hertz $W/Hz$)
as $\sigma^2 = N_0/2$. If the energy per dimension is $\bar{E_s} = E_s/2$, then
the \gls{SNR} is defined as:

\begin{align}
  \gamma_s = SNR = \frac{\bar{E_s}}{\sigma} = \frac{E_s}{2\sigma} = \frac{E_s}{N_0}
\end{align}

\Gls{SNR} can also be defined in terms of the power of the received signal $P_s$
over the power of the noise $P_n = N_0 B$, where $B = 1/T$ is the \gls{BW} of
the receiver. Note, the received signal power $P_s$ relates to the energy per
symbol as $P_s = E_s/T$ for a symbol time T.

\begin{align}
  \gamma_s = SNR = \frac{P_s}{P_n}= \frac{E_s/T}{N_0 B} = \frac{E_s}{N_0}
\end{align}

The \gls{SNR} also has an equivalent metric, the per-bit \gls{SNR} $Ebb-N_0$
expressed in terms of the energy per bit $E_b$ over the noise \gls{PSD} $N_0$.
The energy per bit is $E_b = E_s/\log _{2} M$. Also, define the bit-rate as $R =
  \frac{\log _{2} M}{T}$.

\begin{align}
  \gamma_b = Ebb-N_0 = \frac{E_b}{N_0} = \frac{ E_s/\log _{2} M}{N_0} = \frac{\gamma_s}{\log _{2} M} = \gamma_s \frac{B}{R}
\end{align}

\section{Probability of Error}
TODO

The probability of error $P_s$ is defined in a per-symbol basis. Each constellation has a different $P_s$, seen in the table below based on the Nearest Neighbor bound.

\begin{table}[htbp]
  \centering
  \caption{}
  \begin{tabular}{lcccc}                                                                                \\
    \cmidrule(r){1-3} & $P_s(\gamma_s)$                                  & $P_b(\gamma_b)$ \\
    \midrule MPAM     & $2(1-1/M)Q(\sqrt{\frac{3\gamma_s}{M^2-1}})$      &                 \\
    \midrule MPSQ     & $2Q(\sqrt{2\gamma_s}\sin(\pi/M))$                                  \\
    \midrule MQAM     & $4(1-1/\sqrt{M})Q(\sqrt{\frac{3\gamma_s}{M-1}})$                   \\
    \midrule FSK      & $(M-1)Q(\sqrt(\gamma_s/2))$                                        \\
    \\

    \bottomrule
  \end{tabular}
  \label{tab:constellation_pe}
\end{table}

Useful approximations for $0 \leq \gamma_s \leq 30$ dB:
\begin{itemize}
  \item MQAM $M \geq 4$ has $P_b(\gamma_s) \approxeq 0.2 e^{\frac{-1.5\gamma_s}{M-1}}$
  \item BPSK has $P_b(\gamma_s) = P_s(\gamma_s) \approxeq 2 e^{-1.5\gamma_s}$
\end{itemize}

\printglossary[type=\acronymtype,title=Acronyms]
